### 2014-10-22 fundamentals/examples.tex
better tables

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can be 
improved by

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item and the tools in the \Cyclus toolkit.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosytem.

@@

\subsubsection{External Modules}
External modules have been 
\cite{cyder,separations,streamblender,mktdriveninst,commodconverter} and are 
being \cite{britelite,utk} developed for contribution to the cyclus ecosystem 
of models.

>>>>

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus posesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosytem.

@@

\subsubsection{Supplementary Projects}

A number of projects and tools outside of the core simulation kernel have been 
developed which improve the scope and the diversity of the capabilities in the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.
\begin{table}
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{cycic}\\
Cyclist & Interactive data exploration environment & \cite{cyclist} \\
Ciclus & Continuous Integration scripts for \Cyclus & \cite{ciclus}\\
Cycstub & Skeleton for clean slate module development & \cite{cycstub}\\
Cyan & \Cyclus analysis tool & \cite{cyan}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{cloudlus} \\
\hline
\end{tabularx}
\caption{Many tools outside of the scope of the \Cyclus kernel have been 
developed for improved user, developer, and analyst experinces with \Cyclus.}
\label{tab:coretools}
\end{table}

\subsubsection{Archetype Contributions}

Many archetypes external to the \Cycamore library  
have been \cite{huff_cyder_2013,,streamblender,commodconverter} 
and are being \cite{britelite,utk,mktdriveninst} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.

\begin{table}
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Brite-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{brightlite} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{NFIM} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{commodconverter} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{mktdriveninst} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{streamblender} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{streamblender} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse 
needs of researchers at various institutions. These archetypes, contributed 
outside of the \Cyclus core and \Cycamore libraries are the first demonstration 
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

### 2014-10-22 fundamentals/impl.tex
better tables

\Cycamore \cite{carlsen_cycamore_2014} contains a number of useful facility, 
region, and institution archetypes. 
As future contributions are vetted, the capabilities in \Cycamore may grow. 
However, the current \Cycamore release provides only 
basic functionality, enabling simple fuel cycle analyses. 
\Cycamore is provided so that users can get started quickly with simple 
analyses.

@@

\begin{figure}[htbp!]
\begin{center}
<diagram of a possible Cycamore-only simulation>
\end{center}
\caption{A simple once-through fuel cycle possible with only \Cycamore and 
\Cyclus.}
\label{fig:<+label+>}
\end{figure}<++>

>>>>

\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional modules 
repository, provides a fundamental set of agent archetypes for basic simulation 
functionality within \Cyclus.  Since the \Cyclus framework relies on external 
archetypes to represent the agents within a simulation, \Cycamore provides the 
basic archetypes a new user needs to get started running simple simulations.  
These archetypes support a minimal set of fuel cycle simulation goals and 
provide, by example, a guide to new developers who would seek to contribute 
their own archetypes outside of \Cycamore.

As of version 1.0, \Cycamore contains four facility archetypes, one region 
archetype, and two institution archetypes. Short descriptions of those 
functions can be found in Table \ref{tab:cycamore}.

\begin{table}
\centering
\begin{tabularx}{\textwidth}{|r|l|l|}
\hline
\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}

As future contributions are vetted, the capabilities in \Cycamore may grow. 
However, the current \Cycamore release provides only 
basic functionality, enabling simple fuel cycle analyses. 
\Cycamore is provided so that users can get started quickly with simple 
analyses.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/simplesim}
\end{center}
\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
\label{fig:simplesim}
\end{figure}<++>
